---
title: "Open files in R studio"
output: html_notebook
---

```{r}
# Clear variables
rm(list=ls())
# Get path
path<-getwd(); path # wd means work directory 
# Set path
setwd(path)
```


```{r}
install.packages("readr")
install.packages("readxl")
install.packages("utils")
```


```{r}
library(readr)
library(readxl)
library(utils)
```


# Open the xlsx file like:
```{r}
Example_xlsx_Data <- read_excel("Example_xlsx_Data.xlsx")

Example_xlsx_Data
```


or

...

```{r}
Data <- read_excel("Example_xlsx_Data.xlsx", 
    sheet = "Sheet1")

Data
```



# Open the csv file like:

The csv files are sensible, do not alter them before opening in the R.
```{r}
Data <- read.csv("Example_csv_Data.csv")
Data
```
or

... I will show you how to call the file in the R studio
```{r}
Example_csv_Data <- read_csv("Example_csv_Data.csv")

Example_csv_Data
```


# Open the txt file like:
```{r}
Data <- read.delim("Example_txt_Data.txt")
Data
```


or

... I will show you how to call the file in the R studio




LASTLY, how to save the data as a RData (R workspace) and how to open afterwards:

# Save as RData
```{r}
save(Data, file = "Data.RData") # the data will be saved in the paste 
```


# Open the Rdata
```{r}
# In the document to call this file you just need to code:
load('Data.RData')
```

or

... I will show you how to call the file in the R studio


see the data:
```{r}
Data
```






